\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Nokia}{Sept. 2025 -- Dec. 2025}
      {Firmware Engineering Intern}{Ottawa, Ontario}
      \resumeItemListStart
        \resumeItem{Built \textbf{C++} device initialization service for a new optical transceiver ASIC, optimizing boot sequence control across hardware modules.} % add some figure about latency improvement/performance optimzations: "optimizating boot sequences and reducing X by Y%/sec/."
        \resumeItem{Eliminated packet corruption in a critical \textbf{C++} message-passing utility with 128-bit atomic operations, \textbf{resolving race conditions} and ensuring data integrity.}
        \resumeItem{Resolved \textbf{10+} major defects in the ASIC SDK by analyzing firmware trace logs, reducing daily crash frequency to \textbf{zero}.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Ford Motor Company}{Jan. 2025 -- Apr. 2025}
      {Software Development Intern}{Waterloo, Ontario}
      \resumeItemListStart
        \resumeItem{Created a modular library in \textbf{Python} to simplify and scale testing for an in-vehicle security daemon, reducing reliance on external tooling.}
        \resumeItem{Refactored a deprecated generator utility to integrate with new \textbf{Python} test infrastructure, enabling and enhancing new testing workflows for \textbf{100+ engineers}.}
        \resumeItem{Reworked \textbf{30+} legacy tests to utilize the new library, standardizing test structure for \textbf{all downstream developers}.}
      \resumeItemListEnd
      
    \resumeSubheading
      {NCR Voyix}{May 2024 -- Aug. 2024}
      {Software Engineering Intern}{Waterloo, Ontario}
      \resumeItemListStart
        \resumeItem{Integrated an internal \textbf{Python} query utility into a new patch management system, enabling automatic device data retrieval.}
        \resumeItem{Instrumented a service to validate per-device network compliance data for use \textbf{organization-wide}.}
        \resumeItem{Developed a cross-platform patch verification tool serving \textbf{10,000+} devices across \textbf{10+} platforms.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd