\cvsection{Experience}

\begin{cventries}
%  \cventry
%     {University of Waterloo} % Job title
%     {Research Assistant} % Organization
%     {Waterloo, ON} % Location
%     {Sept. -- Dec. 2024} % Date(s)
%     {
%         \begin{cvitems} % Description(s) bullet points
%             \item {Developed a logic synthesis algorithm to optimize pre-synthesis \textbf{Verilog} circuits.} % Description(s) bullet points
%         \end{cvitems}
%     }

        
 \cventry
    {NCR Voyix} % Job title
    {Systems Software Engineering Intern} % Organization
    {Waterloo, ON} % Location
    {May -- August 2024} % Date(s)
    {
        \begin{cvitems}
            \item {Designed and maintained various systems to support critical engineering infrastructure.}
            \item {Created an internal tool with \textbf{Django} to verify patch compliance for over \textbf{10000} devices.}
            \item {Refactored \textbf{Python} scripts to periodically update internal documents with correct user information.}
        \end{cvitems}
    }
    
 \cventry
    {UW Orbital} % Job title
    {Firmware Developer} % Organization
    {Waterloo, ON} % Location
    {July 2023 -- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Developed a thermal monitoring system and essential functions for command \& data handling.}
	    \item {Leveraged \textbf{FreeRTOS} to develop an event handler for fatal over-temperature shutdowns.}
        \item {Improved system resiliency by integrating stack overflow handling and interrupt service logging.}
      \end{cvitems}
    }

 \cventry
    {Laurel Heights Secondary School Electric Vehicle Club} % Job title
    {Electrical and Telemetry Lead} % Organization
    {Waterloo, ON} % Location
    {Sept. 2022 -- June 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Designed, assembled, and maintained the electrical systems of student-built electric vehicles.}
	    \item {Implemented a telemetry system by interfacing a radio frequency module with \textbf{Arduino}.}
        \item {Competed in the Waterloo Electric Vehicle Challenge, placing \textbf{1st} in the 24-volt category.}
      \end{cvitems}
    }
    
\end{cventries}
