\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Nokia}{Sept. 2025 -- Dec. 2025}
      {Firmware Engineering Intern}{Ottawa, Ontario}
      \resumeItemListStart
        \resumeItem{Built a \textbf{C++17} abstraction layer to translate ASIC configuration tuples into scalable SDK representations, supporting critical initialization and boot utilities across \textbf{20+} operating modes for \textbf{50+ engineers}.}
        \resumeItem{Eliminated packet corruption in a critical \textbf{C++} message-passing utility using 128-bit atomic operations, \textbf{resolving race conditions} and ensuring data integrity.}
        \resumeItem{Implemented isolated ADC/DAC initialization and configuration, enabling \textbf{targeted debugging} of the ASIC datapath beyond full chip bring-up for \textbf{all downstream customers}.}
        \resumeItem{Resolved \textbf{10+} major defects in the SDK by analyzing firmware trace logs, reducing daily crash frequency to \textbf{zero}.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Ford Motor Company}{Jan. 2025 -- Apr. 2025}
      {Software Development Intern}{Waterloo, Ontario}
      \resumeItemListStart
        \resumeItem{Designed and implemented \textbf{Python} libraries to fuzz ECU access tokens, enabling native security testing of a daemon deployed across \textbf{all production ECUs}.}
        \resumeItem{Integrated new libraries into automated testing pipelines, enhancing validation workflows and eliminating reliance on \textbf{external tooling}.}
        \resumeItem{Migrated \textbf{30+} legacy tests to the new libraries and integrated with existing \textbf{Python} infrastructure, standardizing security workflows for \textbf{100+ engineers}.}
      \resumeItemListEnd
      
    \resumeSubheading
      {NCR Voyix}{May 2024 -- Aug. 2024}
      {Software Engineering Intern}{Waterloo, Ontario}
      \resumeItemListStart
        \resumeItem{Integrated a \textbf{Python} query utility into a patch management system, reducing manual retrieval time by \textbf{60\%} and enabling automation for \textbf{ 80+} daily requests.}
        \resumeItem{Instrumented a service to validate per-device network compliance data for use \textbf{organization-wide}.}
        \resumeItem{Developed a cross-platform patch verification tool serving \textbf{10,000+} devices across \textbf{10+} platforms.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd